Notes on Wide Gap

### 2016-05-13 paper/wide_gap_notes.tex
preliminary B-field first order plot
notes on lack of neutral mode

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/u_near_threshold_test}
\caption{Wide-gap first-order velocity perturbations near threshold. Unnormalized. This is with Q = 0.05, Rm = 0.85, but we now know that critical parameters are closer to Rm = 0.845, Q = 0.006 (finer grid running now).
\label{fig:firstorder_u}}
\end{figure}

@@

@@

>>>>

@@

The purely conducting boundary condition states that the axial component of the current ($\mathbf{J}_z = [\nabla \times \mathbf{B}]_z)$ must be zero at the walls. In the thin gap geometry, the purely conducting boundary condition on the azimuthal magnetic field is $\partial_x(B_y) = 0$ for axisymmetric perturbations. A spatially constant azimuthal field satisfies both the thin-gap MRI equations and this boundary condition. This neutral mode is formally included in the analysis of Umurhan et al 2007 and yields a second amplitude equation in the form of a simple diffusion equation. This amplitude equation decouples from the GLE because of the translational symmetry of the thin-gap geometry. Because that symmetry is not preserved in the wide-gap case, Umurhan et al postulate that slow variation in the wide-gap geometry will be governed by two coupled amplitude equations. However, the wide-gap conducting boundary condition $J_z = \frac{1}{r} \partial_r (r B_\phi) = 0$, together with the purely geometric term in Equation \ref{eq:By_perturbed}, conspire to prevent the wide-gap geometry from sustaining a neutral mode.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/u_near_threshold_test}
\caption{Wide-gap first-order velocity perturbations near threshold. Unnormalized. This is with Q = 0.05, Rm = 0.85, but we now know that critical parameters are closer to Rm = 0.845, Q = 0.006 (finer grid running now).
\label{fig:firstorder_u}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../../weakly_nonlinear_mri/python/widegap/figures/B_near_threshold_test}
\caption{Wide-gap first-order B-field perturbations near threshold. Unnormalized. This is with Q = 0.05, Rm = 0.85, but we now know that critical parameters are closer to Rm = 0.845, Q = 0.006 (finer grid running now).
\label{fig:firstorder_B}}
\end{figure}
